Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-13 tex/sections/blocks.tex
Add more explanation for "Emergency Forking"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon network uses a parallel algorithm to produce block certificates and therefore the signature scheme needs
to satisfy certain properties:
\begin{itemize}
    \item \textbf{Associative aggregation:} the signature aggregation operator is associative.
    \item \textbf{Efficient cancellation:} if $S$ is the predefined set of users that we need their aggregate
    signature, verifying an aggregate signature of $S-U$ can be done in time $O(T+|U|)$, if the aggregate
    signature of $S$ can be verified in $O(T)$.
\end{itemize}

@@

For validating the previous block, instead of directly validating the contents of the block, a validator only
verifies the block certificates. Each block of the Argennon blockchain has two certificates: the certificate of
validators, $v \mhyphen cert$, and the certificate of delegates, $d \mhyphen cert$. Verifying $d \mhyphen
cert_{h-1}$ is straightforward but verifying $v \mhyphen cert_{h-1}$ is more challenging. $v \mhyphen cert_{h-1}$ is an
aggregate signature and validating it requires accessing the AscEE heap state at block~$h-1-m$, where $m$ is the
total number of validator assemblies, to obtain public keys and stake values. Again, in addition to direct
verification, a validator can use computational integrity proofs, received from the Argennon cloud, to perform
cheaper verification of this certificate.

>>>>

The Argennon network uses a parallel algorithm to produce block certificates and therefore the signature scheme needs
to satisfy certain properties:
\begin{itemize}
    \item \textbf{Associative aggregation:} the signature aggregation operator is associative.
    \item \textbf{Efficient cancellation:} if $S$ is a predefined and fixed set of users and $U$ is an arbitrary subset
    of~$S$, verifying an aggregate signature of $S-U$ can be done in time $O(T+|U|)$, if the aggregate
    signature of $S$ can be verified in $O(T)$.
\end{itemize}

@@

For validating the previous block, instead of directly validating the contents of the block, a validator only
verifies the block certificates. Each block of the Argennon blockchain has two certificates: the certificate of
validators, $v \mhyphen cert$, and the certificate of delegates, $d \mhyphen cert$. Verifying $d \mhyphen
cert_{h-1}$ is straightforward but verifying $v \mhyphen cert_{h-1}$ is more challenging. $v \mhyphen cert_{h-1}$ is an
aggregate signature and validating it requires accessing the staking database at block~$h-1-m$, where $m$ is the
total number of validator assemblies, to obtain public keys and stake values. Again, in addition to direct
verification, a validator can use computational integrity proofs, received from the Argennon cloud, to perform
cheaper verification of this certificate.

### 2023-01-13 tex/sections/consensus.tex
Add more explanation for "Emergency Forking"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

As we mentioned before, the block with height $h$ needs a certificate from the assembly of
validators with index $h$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity of the block (See Section~\ref{subsec:block-validation}), and if the block is valid, he issues
an ``accept'' signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validator assembly of the previous block.
Some validators may also require seeing a certificate from
some community based committees. An honest validator never signs a certificate for two different blocks with the
same height.

@@

We assume that an adversary is able to fully control message transmission between users and is able to partition the
network arbitrarily for finite periods of time. Under these circumstances, the recovery protocol can recover the
functionality of the Argennon blockchain as long as more than $2/3$ of the total stake of every validator assembly is
controlled by honest users. The recovery protocol uses two main emergency procedures to
recover the functionality of the Argennon blockchain: \emph{emergency forking} and \emph{emergency
agreement} protocol.

@@

For forking at block $h$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $h$.
The height of the fork block therefore is $h + 1$, and the fork block needs a valid certificate from the assembly of
validators with index $h+1$ modulo $m$. When a
fork block gets certified by validators, its parent is also confirmed and will become a part of the blockchain, even if
it does not have a validators certificate.

@@

For forking the blockchain, the reserve committee uses a straightforward algorithm: let $h_v$ be the height of the last
block with a validator certificate and $h_v+k$ be the height of the last valid block that the reserve committee has
seen. For forking the main chain, the reserve committee generates all fork blocks with heights $h_v+1,h_v+2,\dots,
h_v+k+1$. The parent of the fork block with height $h_v+i$ will be the block $h_v+i-1$ of the main chain. The
reserve committee will wait until the fork block with height $h_v+k+1$ receives a certificate from validators and
then will continue the normal chain after that fork block. Hence, the fork block with height $h_v+k+1$
will be the parent of the first normal block generated by the reserve committee.

@@

If $h_{\max}$ denotes the height of the highest block with a validators certificate, as long as more than $2/3$ stake
of every assembly of validators are honest, for a fork block with height $h_f$ we have:\footnote{This fork block
forks the blockchain at height $h_f-1$.}
\begin{itemize}
    \item if $h_f \leq h_{\max}$, the fork block can not receive a certificate from validators.
    \item if $h_f = h_{\max} + 1$, the fork block may receive a certificate from validators or not. It is possible that
    the validators of the assembly with index $h_f$ modulo $m$ get divided between the fork block and a block at
    height $h_f$ of the main chain.
    \item if $h_f = h_{\max} + 2$, the fork block can always receive a certificate from validators, if network
    partitions do not last forever.
    \item if $h_f \geq h_{\max} + 3$, the fork block can always receive a certificate from validators \textbf{only if} a
    fork block at height $h_f-1$ gets certified by validators.
\end{itemize}

Consequently, if two fork blocks at heights $h_0$ and $h_0+k$ are generated by the reserve committee, if both blocks
receive a certified from validators, we must have $h_0 > h_{\max}$, and there must exist fork blocks with heights
$h_0+1,\dots,h_0+k-1$ which are certified by validators. That means if a malicious reserve committee generates a normal
block after any fork block with height less than $h_0+k$, that normal block can not receive a certificate from
validators.

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block whose parent is block $b_2$ and that will essentially discard $b_1$. Notice
that if a block at height $h+1$ had been certified by validators the fork block could not have received a certificate
from validators.

>>>>

Having multiple assemblies gives validators some ``resting'' time and allows a validator to be out of sync with the
network for some time, without losing the opportunity to vote for any blocks.

@@

As we mentioned before, the block with height $h$ needs a certificate from the assembly of
validators with index $h$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity of the block (See Section~\ref{subsec:block-validation}), and if the block is valid, he issues
an ``accept'' signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast
the signature \textbf{only after} he sees the certificate of the validator assembly of the previous block.
Some validators may also require seeing a certificate from
some community based committees. An honest validator never signs a certificate for two different blocks with the
same height.

@@

We assume that an adversary is able to fully control message transmission between users and is able to partition the
network arbitrarily for finite periods of time. Under these circumstances, the recovery protocol can recover the
functionality of the Argennon blockchain as long as more than $2/3$ of the total stake of every validator assembly is
controlled by honest users. The recovery protocol uses two main emergency procedures to
recover the functionality of the Argennon blockchain: the \emph{emergency forking} and \emph{emergency
agreement} protocol.

@@

For forking at block $h$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $h$.
The height of the fork block therefore is $h + 1$, and the fork block needs a valid certificate from the assembly of
validators with index $h+1$ modulo $m$. When a
fork block gets certified by validators, its parent is also confirmed and will become a part of the blockchain, even if
it does not have a certificate of validators.

@@

For forking the blockchain, the reserve committee uses a straightforward algorithm: let $h_v$ be the height of the last
block with a validator certificate and $h_v+k$ be the height of the last valid block that the reserve committee has
seen. For forking the main chain, the reserve committee generates all fork blocks with heights~$h_v+1,h_v+2,\dots,
h_v+k+1$. The parent of the fork block with height $h_v+i$ will be the block~$h_v+i-1$ of the main chain. The
reserve committee will wait until the fork block with height~$h_v+k+1$ receives a certificate from validators and
then will continue the normal chain after that fork block. Hence, the fork block with height~$h_v+k+1$
will be the parent of the first normal block generated by the reserve committee.

@@

If $h_{\max}$ denotes the height of the highest block with a validators certificate, as long as more than $2/3$ stake
of every assembly of validators is honest, for a fork block with height $h_f$ we have:\footnote{This fork block
forks the blockchain at height $h_f-1$.}
\begin{itemize}
    \item if $h_f \leq h_{\max}$, the fork block can not receive a certificate from validators.
    \item if $h_f = h_{\max} + 1$, when there is no main block with height~$h_f$, the fork block can always receive a
    certificate from validators, otherwise the fork block may receive a certificate or not. It is possible that
    the validators of the assembly with index $h_f$ modulo $m$ get divided between the fork block and a block at
    height $h_f$ of the main chain.
    \item if $h_f = h_{\max} + 2$, the fork block can always receive a certificate from validators, if network
    partitions do not last forever.
    \item if $h_f \geq h_{\max} + 3$, the fork block can always receive a certificate from validators \textbf{only if} a
    fork block at height $h_f-1$ gets certified by validators.
\end{itemize}

The reserve committee does not know the value of $h_{\max}$. However, if the reserve committee creates all fork blocks
with heights~$h_0,h_0+1,h_0+2,\dots$ every fork block with height $h \geq h_{\max} + 2$ will surely get a certificate.
If there is no block in the main chain with height~$h_{\max} + 1$, then the fork block with height~$h_{\max} +
1$ will also get a certificate, otherwise the reserve committee should be able to eventually find the main block
at $h_{\max}+1$ and generate a fork block with height~$h_{\max} + 2$ as its successor. This way, the reserve
committee will always be able to create at least one fork block which gets certified and continue the chain after the
fork block with the highest height.

If two fork blocks at heights $h_0$ and $h_0+k$ are generated by the reserve committee and both blocks receive a
certified from validators, we must have $h_0 > h_{\max}$, and there must exist fork blocks with heights
$h_0+1,\dots,h_0+k-1$ which are certified by validators. That means if a malicious reserve committee generates a normal
block after any fork block with height less than $h_0+k$, that normal block can not receive a certificate from
validators.

If a malicious reserve committee creates two fork blocks with the same height, either only one of
them can get a certificate, which makes the other one ineffective or validators get split between blocks
and the chain will halt. In this case the emergency agreement protocol will start.

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block whose parent is block $b_2$, that will essentially discard $b_1$. Notice
that if a block at height $h+1$ had been certified by validators the fork block after $b_2$ could not have received a
certificate from validators.
